Analysing the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd

We conclude that Donald Trump have $6.6\%$ probability of winning this election. From our prediction, we highlight North Carolina as the most important battleground state. The state has a predicted $14.2\% $probability to be won by Trump, and will give him 16 electoral votes. Along with the votes that we predict he will almost certainly gain, this pushes him one step (9 electoral votes) to victory. This provide powerful guidence to how campaign and fund raising strategies should be targeted on the election day. And provides a forecast on one of the most important influences in economy in the next several months, which will be especially helpful in planning market stragities.

The scripts in this paper are written in R[@citeR], The table in our study are generated by knitr [@knitr],  and graph with ggplot2[@ggplot2]. Data input and output were done using arrow[@arrow], and curl[@curl]. Data cleaning made use of janitor[@janitor].

>>>>

We conclude that Donald Trump have $6.6\%$ probability of winning this election. From our prediction, we highlight North Carolina as the most important battleground state. The state has a predicted $14.2\%$ probability to be won by Trump, and will give him 16 electoral votes. Along with the votes that we predict he will almost certainly gain, this pushes him one step (9 electoral votes) to victory. This provide powerful guidence to how campaign and fund raising strategies should be targeted on the election day. And provides a forecast on one of the most important influences in economy in the next several months, which will be especially helpful in planning market stragities.

The scripts in this paper are written in R[@citeR],  using mainly tidyverse[@tidyverse] The table in our study are generated by knitr [@knitr],  and graph with ggplot2[@ggplot2]. Data input and output were done using arrow[@arrow], and curl[@curl]. Data cleaning made use of janitor[@janitor].
